Generalized Linear Mixed Models

### 2009-04-02 docs/inla/inla.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@172 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}
\frametitle{Example:bacteria}
<<bacmcmc,fig=false,echo=true>>=
library(glmmBUGS)
bac = glmmBUGS(y ~ trt, effects='ID', family='binomial',data=bacteria, file='modelx.bug')
startingValues = bac$startingValues
source("getInits.R")
library(BRugs)
library(R2WinBUGS)
bacResult = bugs(bac$ragged, getInits, 
	parameters.to.save = names(getInits()),
  model.file="model.bug", n.chain=3, n.iter=1000, n.burnin=100, n.thin=10,
                             program="openbugs") 
bacParams = restoreParams(bacResult, bac$ragged)

@@

\begin{frame}
\frametitle{Example: }
<<bacteriaINlA>>=
# do this pql = glmmPQL(y ~ trt, random = ~1|ID, family='binomial',data=bacteria)

@@

\begin{frame}
\frametitle{Example: Lung cancer in Ontario}
<<cancerInla>>=
if(F) {
library(diseasemapping)
library(sp)
data(popdata)
data(casedata)
model = getRates(casedata, popdata, ~age*sex)
ontario = getSMR(popdata,model,  casedata)
data(popDataAdjMat)

>>>>

\begin{frame}
\frametitle{Example:bacteria}
<<bacmcmc,fig=false,echo=true>>=
library(glmmBUGS)
bac = glmmBUGS(y ~ trt, effects='ID', family='binomial',data=bacteria, file='modelx.bug')
startingValues = bac$startingValues
source("getInits.R")
library(BRugs)
library(R2WinBUGS)
bacResult = bugs(bac$ragged, getInits, 
	parameters.to.save = names(getInits()),
  model.file="model.bug", n.chain=3, n.iter=100, n.burnin=10, n.thin=2,
                             program="openbugs") 
bacParams = restoreParams(bacResult, bac$ragged)

@@

\begin{frame}
\frametitle{Example: }
<<bacteriaINlA,fig=false>>=
#library(MASS)
#data(bacteria)
#bacterianew <- bacteria[,-(2:3)]
#bacterianew$y = as.integer(bacteria$y=="y")
#levels(bacterianew$trt) <- c("placebo", "drug", "drugplus")
#bacteria=bacterianew
# do this pql = glmmPQL(y ~ trt, random = ~1|ID, family='binomial',data=bacteria)

@@

\begin{frame}
\frametitle{Example: Lung cancer in Ontario}
<<cancerInla,fig=false>>=
if(F) {
library(diseasemapping)
library(sp)
data(popdata)
data(casedata)
model = getRates(casedata, popdata, ~age*sex)
ontario = getSMR(popdata,model,  casedata)
data(popDataAdjMat)
